\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-23 paper.tex
added subsection on code generation

Embedded systems are a prime example of an environment where code needs to be
of a high quality.

Code Generation for embedded systems/WSNs \cite{leupers2000code,marwedel2002code}

Code Optimization for embedded systems/WSNs \cite{panda2001data,naik2001software}

Code Generation for IDS \cite{charitakis2003code}

% manet: IDS algorithms -> coorporation, trust

More than in a classic network IDS, ID algorithms for MANETS operate with a
large degree of uncertainty. They often have to collaborate with other devices
in the network \cite{marchang2008collaborative,krontiris2009cooperative}, which
increases the level of uncertainty, because no other device can fully be
trusted. An IDS on an IoT device will be able to provide the services with
information about the reputation \cite{ganeriwal2008reputation} of other nodes
in the network.

>>>>

Embedded systems are a prime example of an environment where code needs to be
of a high quality. Focus on size and performance are a logical choice when
dealing with limited storage and processing power. Different techniques are
described in literature and implemented in compilers, starting at the lowest
level\cite{leupers2000code, marwedel2002code}.

Optimizing for power efficiency however proves to be concurrent to size and
performance optimization. Different strategies are needed. Data and memory
optimizations \cite{panda2001data} can result in interesting improvements on a
lower level. But to really preserve energy higher-level strategies are
required, targeting architecture, radio handling, efficient
software,\dots\cite{naik2001software}. Most of these are beyond the control of
the compiler and show that a higher level of abstraction is required to address
them.

DSLs are a solution here, but other paradigms are possible. A mixed framework
consisting of a virtual machine (VM) and native code
extension\cite{sadilek2007energy}, combined with energy-aware compilation,
seems a promising approach. By offloading the optimization to a VM and only
compiling parts and not the whole, the solution allows updating at a very
granular scale, thus reducing the update cost, while maintaining flexibility
and lowering the development effort. As stated in the introduction, \NAME
focuses on the reduction of the development effort, while preserving
flexibility.

Finally, applying code generation to IDS, typically tries to generate native
code to avoid the interpretation of the description of patterns.
I2S\cite{charitakis2003code} is an example that generates code for
SNORT\cite{roesch1999snort} rules. To optimise this highly efficient code, it
often targets a specific platform.
